ManuscriptTargetProtein

### 2024-02-15 Code/ManuscriptTargetProtein.Rmd
fix target protein file names

TargetProtein <- TargetProtein %>%
  rename(SampleID = "ï..Sample")

@@

MIT9313ProteinAnotated <- TargetProtein %>%
  filter( Strain == "MIT9313") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.6, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MIT9313ProteinAnotated

MED4ProteinAnotated <- TargetProtein %>%
  filter( Strain == "MED4") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MED4ProteinAnotated
```

@@

 ggsave(file = file.path(PlotsOut, paste("MED4ProteinAnotated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAnotated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

TargetProtein <- TargetProtein %>%
  rename(SampleID = "Sample")

@@

MIT9313ProteinAnnotated <- TargetProtein %>%
  filter( Strain == "MIT9313") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.6, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MIT9313ProteinAnnotated

MED4ProteinAnnotated <- TargetProtein %>%
  filter( Strain == "MED4") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MED4ProteinAnnotated
```

@@

 ggsave(file = file.path(PlotsOut, paste("MED4ProteinAnnotated",".png",sep = "")), plot = MED4ProteinAnnotated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAnnotated",".png",sep = "")), plot = MIT9313ProteinAnnotated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
